---
title: "v3_HTS_review_2020"
author: "Dr Marriott Nliwasa"
date: "24/02/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

***
## 1. Background
This document is an analysis of **TB** and **HIV** screening among *adults with symptoms of TB*

<br>
These are the main outcomes:

1. HIV outcomes
- prevalence of HIV
- number needed to screen to detect one HIV positive case
- description of HIV testing strategies
2. TB outcomes 
- prevalence of TB
3. Ratio of HIV prevalence in TB patients and presumptive TB patients

<br>
This is an updated review [^1]

[^1]: Nliwasa et al. JIAS. 2018 [link](https://www.ncbi.nlm.nih.gov/pmc/articles/PMC6067081/)

## 2. Set-up
Loading necessary packages
```{r echo=F}
.libPaths(c("C:/Users/Marriott Nliwasa/Documents/R/win-library/3.4", .libPaths()))
```

## 3. Load packages

```{r echo=F, cache=FALSE, results=FALSE, warning=FALSE, comment=FALSE, warning=FALSE, warn.conflicts = FALSE, message=F}

#install.packages("dplyr")
#install.packages("meta")
#install.packages("metafor")
#install.packages("ggplot2")
#install.packages("gridExtra")
#install.packages("xlsx")
#install.packages("doBy")
#install.packages("devtools")
#install.packages("ggpmisc")
#install.packages("tidyverse")
#install_github("rstudio/gt")
#install_github("jkmisc")
#install.packages("janitor")
#install.packages("skimr")
#install.packages("ggalt")
#install.packages("here")
#install.packages("forcats")
#install.packages("ellipses")
#install.packages("here")
#install.packages("ggrepel")
#install.packages("gt")
```

```{r echo=T, cache=FALSE, results=FALSE, warning=FALSE, comment=FALSE, warning=FALSE, warn.conflicts = FALSE, message=F}

library(dplyr)
library(ggplot2)
library(gridExtra)
library(metafor)
library(meta)
library(devtools)
library(dplyr)
library(stats)
library(ggpmisc)
library(tidyverse)
library(here)
library(ggrepel)
library(ggalt)
library(forcats)

```

=================================================================

## 4. Importing data
```{r}
reviewdata<-read.csv(here("review2_data/Extended_dataset_v7.csv"))
str(reviewdata)
dim(reviewdata)
```


## 5. Data cleaning

```{r}
df1<-reviewdata
dim(df1)

#create the study label variable
df1$label <- paste(df1$e05_country, df1$e02_author, df1$e04_print_year, sep = ", ")
nrow(df1)
        
#create the sort variable --- by prevalence of HIV in suspects
df1$p <- round((df1$e21_HIV._suspects/df1$e20_susp_scrn),dig=2)
        
#key confounding variables

#*setting-level of care
table(df1$e09_setting)
df1$setting <- factor(df1$e09_setting, levels = c(
  "community", "primary care", "mix","hospital mixed", "hospital inpatient", "hospital outpatient"))
df1$setting[df1$setting=="hospital mixed"]<-"mix" 
df1$setting[df1$setting=="hospital outpatient"]<-"mix"
df1$setting <- factor(df1$setting, levels = c(
  "community", "primary care", "mix", "hospital inpatient"))

table(df1$setting)
        
#*geographical region        
table(df1$e08_subregion)
df1$subregion <- df1$e08_subregion
df1$subregion <- factor(as.character(df1$subregion), levels = c(
  "Americas", "Central Africa", "East Africa", "Southern Africa", "South-East Asia", "West Africa", "Western pacific"))

table(df1$subregion)
        
#*definition suspect
table(df1$e16_suspect_definition)
df1$definition[df1$e16_suspect_definition=="cough any duration or other "]<-"other"
df1$definition[df1$e16_suspect_definition=="cough any duration or other"]<-"other"
df1$definition[df1$e16_suspect_definition=="chronic cough and other"]<-"chronic cough" 
df1$definition[df1$e16_suspect_definition=="chronic cough "]<-"chronic cough"
df1$definition[df1$e16_suspect_definition=="chronic cough"]<-"chronic cough"
df1$definition[df1$e16_suspect_definition=="chronic cough or other"]<-"other"
df1$definition[df1$e16_suspect_definition=="chronic cough or other"]<-"other"
df1$definition[df1$e16_suspect_definition=="clinician identified"]<-"other"
df1$definition[df1$e16_suspect_definition=="any TB symptom"]<-"other"
df1$definition[df1$e16_suspect_definition=="other"]<-"other"
table(df1$definition)
df1$definition <- factor(as.character(df1$definition), levels = c(
  "chronic cough", "other"))

table(df1$definition)

#*individual country
table(df1$e05_country)
df1$e05_country <- factor(as.character(df1$e05_country), levels = c(
  "Botswana", "Cambodia", "DR Congo", "Ethiopia", "G. Bissau", "Ghana", "Haiti", "India" ,"Kenya", "Malawi", "Nepal", 
  "Nigeria", "Peru","Rwanda", "South Africa", "Tanzania", "Thailand", "Uganda", "Zambia", "Zimbabwe"))
table(df1$e05_country)
 
#*HIV prevalence in general population      
summary(df1$e11_countryHIV.)
df1$countryHIVprev<-cut(df1$e11_countryHIV., breaks= c(0, 5, 30), labels = c("low (0-5%)", "high(5-30%)"))
table(df1$countryHIVprev)



#*population-level HIV prevalence (based on region prevalence)
summary(df1$e50_subHIV)
df1$popHIVprev<-cut(df1$e50_subHIV, breaks= c(0, 5, 30), labels = c("low (0-5%)", "high(5-30%)"))
table(df1$popHIVprev)

#*TB screening type
table(df1$e23_tbscrn_type)
df1$tbscreen <- df1$e23_tbscrn_type
table(df1$tbscreen)
df1$tbscreen <- factor(as.character(df1$tbscreen), levels = c("diagnostic", "none", "screening"))
table(df1$tbscreen)

#*group offered HIV
table(df1$e17_offered_HIV)
df1$allHIVoffer <- df1$e17_offered_HIV
table(df1$allHIVoffer)
df1$allHIVoffer <- factor(as.character(df1$allHIVoffer), levels = c(
  "all participants", "other", "participants with symptoms"))
table(df1$allHIVoffer)

#study quality for measuring HIV prevalence
table(df1$e45_qual_HIV)
df1$quality_HIV <- df1$e45_qual_HIV
df1$quality_HIV[df1$e45_qual_HIV=="Unclear risk"]<-"High risk" 
table(df1$quality_HIV)

#study quality for measuring TB
table(df1$e46_qual_TB)
df1$quality_TB <- df1$e46_qual_TB
df1$quality_TB[df1$e46_qual_TB=="Unclear risk"]<-"High risk" 
table(df1$quality_TB)

#ART coverage--where 81% is cut-off for achieving second 90 in 909090

summary(df1$e47_artcov)
hist(df1$e47_artcov)
df1$artcov<-cut(df1$e47_artcov, breaks= c(-0.9, 40, 81), labels = c("low (0-40%)", "moderate(40-81%)"))

table(df1$artcov)

#study mid-year
hist(df1$e03_middatayr)
summary(df1$e03_middatayr)
df1$midyr<-cut(df1$e03_middatayr, breaks= c(2000, 2006, 2011, 2017), labels = c("2001/06","2006/11", "2011/16"))
table(df1$midyr)

```

## 6. Table 1 Characteristics of included studies

```{r}
dim(df1)
df1a<- df1
dim(df1a)

#this section was for generating table 1 of the published review paper

#*number of countries per region
numcountry<-aggregate(df1a["e01_id"], by=df1a[c("e08_subregion","e05_country")], FUN=length)
tab_numcountry<-table(numcountry$e08_subregion)
tab_numcountry
perc_numcountry<- (prop.table(tab_numcountry)*100)
perc_numcountry

#*Number of studies per region
tablerege<-table(df1a$subregion, useNA= "ifany")
tablerege
perc_tablerege<- (prop.table(tablerege)*100)
perc_tablerege

#*definition c2wks per region
num2wk<-aggregate(df1a["e01_id"], by=df1a[c("e08_subregion","definition")], FUN=length)
tab_num2wk<-table(num2wk$definition)
perc_tab_num2wk<- (prop.table(tab_num2wk)*100)
perc_tab_num2wk

#*setting per region
numsetting<-aggregate(df1a["e01_id"], by=df1a[c("e08_subregion","setting")], FUN=length)
tab_numcountry<-table(numsetting$e08_subregion)
tab_numcountry
perc_numcountry<- (prop.table(tab_numcountry)*100)
perc_numcountry

#*median year of study
summary(df1a$e03_middatayr)
medyr<-aggregate(df1a["e03_middatayr"], by=df1a[c("subregion")], FUN=summary)
medyr

#*population HIV prevalence
summary(df1a$e11_countryHIV)
hist (df1a$e11_countryHIV.)
hivpop<-aggregate(df1a["e11_countryHIV."], by=df1a[c("subregion")], FUN=summary)
hivpop

#bubble ART coverage and population HIV

ggplot(df1a, aes(x = e03_middatayr, y = e47_artcov_perc)) + 
  geom_point(aes(color = popHIVprev, size = e16_number_suspects,  label=e05_country), alpha = 1) +
  #geom_text_repel(aes(label = e05_country,  color = popHIVprev), size = 2.5)+
  scale_color_manual(values = c("steelblue", "firebrick")) +
  scale_x_continuous(breaks=c(2001,2002,2003,2004,2005,2006,2007,2008,2009,2010,2011,2012,2013,2014,2015,2016))+
  scale_y_continuous(limits= c(0,100), breaks=c(0,25,50,75, 100))+
  scale_size(range = c(2, 15))+
  theme_bw()
ggsave("df1a.png", dpi=600)


#*number of suspects

aggregate(df1a[c("e16_number_suspects")], by=df1a[c("subregion")], FUN = sum)

sum(df1a$e16_number_suspects)
```

## 7.Uptake of HIV testing

```{r}
#defining uptake
dim(df1a)
df1a$uptake_hiv <-df1a$e20_susp_scrnhiv/df1a$e16_number_suspects*100
summary(df1a$uptake_hiv)
hist(df1a$uptake_hiv)
```

## 11. Relationships
```{r}

df2<-df1a
sum(df2$e16_number_suspects)
sum(df2$e20_susp_scrnhiv)

p<-df2$e21_HIV._suspects/df2$e20_susp_scrnhiv
summary(df2$p)

#graph1
df2$hiv_prev_in_tb_symptoms<-df2$e21_HIV._suspects/df2$e20_susp_scrnhiv
df2$hiv_prev_in_tb_cases<-df2$e28_n_HIVposTB/df2$e27_Tbcases_HIVden
df2a<-subset(df2, df2$hiv_prev_in_tb_cases !="NA" & setting=="community")
df2a<-subset(df2, df2$hiv_prev_in_tb_case !="NA")

df2a %>%
ggplot() +
geom_dumbbell(aes(y=fct_reorder(df2a$label, df2a$hiv_prev_in_tb_symptoms),
  x=df2a$hiv_prev_in_tb_symptoms, xend=df2a$hiv_prev_in_tb_cases), size=2,
  dot_guide = TRUE, dot_guide_size = 0.25,
  colour_x = "steelblue", colour_xend = "firebrick", colour = "steelblue") +
  scale_x_continuous(labels = scales::percent, limits = c(0,1)) +
  theme_bw()+
    theme(axis.title.x=element_blank(),axis.title.y=element_blank())+
   facet_wrap(.~factor(df2a$setting), scales = "free_y")
ggsave("df2a.png", width = 7.29, height = 6.0)
```

##Table 4 analysis
```{r}
df2b<- select(df2, e01_id, label, e21_HIV._suspects, e20_susp_scrnhiv,setting, e11_countryHIV., countryHIVprev, subregion, definition, e28_n_HIVposTB, e27_Tbcases_HIVden, midyr, quality_HIV, artcov, e50_subHIV_perc,  popHIVprev, p, studytbhivprev)

df2b<- subset(df2b, studytbhivprev != "NA")

write.csv(df2b, file = "C:/Users/Marriott Nliwasa/Dropbox/R/working_file/df2_hiv.csv", row.names = TRUE, na = "")

dim(df2b)

#prevalence ratios by


table(df2b$setting)


#g1---Forest plot of HIV prevalence by level of care

#presumptive
tiff("g1a.tiff", height=20, width=11, units="in", res=300, compression="lzw")
forest(metaprop(e21_HIV._suspects, e20_susp_scrnhiv, studlab= label, title="HIV prevalence in adults with TB symptoms", byvar=setting, comb.fixed=T, comb.random=T, sm="PAS", data=df2b), 
       sortvar=df2b$p, xlim=c(0, 100), fontsize=14, pscale=100, pooled.totals=T, pooled.events=T, print.tau2=T, print.I2=T, digits=1, 
  leftcols = c("studlab", "n"), 
  rightcols = c("effect", "ci", "w.random"), 
  leftlabs = c("Study", "N"), rightlabs= c("Prev.(%)", "95% CI", "w.random"), 
  xlab = "HIV Prevalence (%)", lwd =1, just="right", col.diamond = "black", col.by = "black")
dev.off() 


#TB patients
tiff("g1b.tiff", height=20, width=11, units="in", res=300, compression="lzw")
forest(metaprop(e28_n_HIVposTB, e27_Tbcases_HIVden, studlab= label, title="HIV prevalence in adults with TB symptoms", byvar=setting, comb.fixed=T, comb.random=T, sm="PAS", data=df2b), 
       sortvar=df2b$p, xlim=c(0, 100), fontsize=14, pscale=100, pooled.totals=T, pooled.events=T, print.tau2=T, print.I2=T, digits=1, 
  leftcols = c("studlab", "n"), 
  rightcols = c("effect", "ci", "w.random"), 
  leftlabs = c("Study", "N"), rightlabs= c("Prev.(%)", "95% CI", "w.random"), 
  xlab = "HIV Prevalence (%)", lwd =1, just="right", col.diamond = "black", col.by = "black")
dev.off() 

#ratio
dfx <- df2b %>%
   mutate(e27_Tbcases_HIVden = as.numeric(e27_Tbcases_HIVden))%>%
  mutate(cases_hivpos = e28_n_HIVposTB,
         cases_hivneg = (e27_Tbcases_HIVden - e28_n_HIVposTB),
         suspect_hivpos = e21_HIV._suspects,
         suspects_hivneg = (e20_susp_scrnhiv - e21_HIV._suspects))

dfy<- subset(dfx, cases_hivpos !="NA" &  cases_hivneg!="NA" &  suspect_hivpos!="NA" & suspects_hivneg !="NA")

#m5<- rma(ai=suspect_hivpos, bi=suspects_hivneg, ci=cases_hivpos, di=cases_hivneg,
               #mods = ~ relevel(subregion,ref='South-East Asia'), data=dfy, measure="PR", #method="REML")

#m5$b <- exp(m5$b)
#m5$ci.lb <- exp(m5$ci.lb)
#m5$ci.ub <- exp(m5$ci.ub)

#summary(m5)

#g2---Forest plot of HIV prevalence by subnational HIV
#presumptive
table(df2b$popHIVprev)

tiff("g2a.tiff", height=20, width=11, units="in", res=300, compression="lzw")
forest(metaprop(e21_HIV._suspects, e20_susp_scrnhiv, studlab= label, title="HIV prevalence in adults with TB symptoms", byvar=popHIVprev, comb.fixed=T, comb.random=T, sm="PAS", data=df2b), 
       sortvar=df2b$p, xlim=c(0, 100), fontsize=14, pscale=100, pooled.totals=T, pooled.events=T, print.tau2=T, print.I2=T, digits=1, 
  leftcols = c("studlab", "n"), 
  rightcols = c("effect", "ci", "w.random"), 
  leftlabs = c("Study", "N"), rightlabs= c("Prev.(%)", "95% CI", "w.random"), 
  xlab = "HIV Prevalence (%)", lwd =1, just="right", col.diamond = "black", col.by = "black")
dev.off() 

#TB patients
tiff("g2b.tiff", height=20, width=11, units="in", res=300, compression="lzw")
forest(metaprop(e28_n_HIVposTB, e27_Tbcases_HIVden, studlab= label, title="HIV prevalence in adults with TB symptoms", byvar=popHIVprev, comb.fixed=T, comb.random=T, sm="PAS", data=df2b), 
       sortvar=df2b$p, xlim=c(0, 100), fontsize=14, pscale=100, pooled.totals=T, pooled.events=T, print.tau2=T, print.I2=T, digits=1, 
  leftcols = c("studlab", "n"), 
  rightcols = c("effect", "ci", "w.random"), 
  leftlabs = c("Study", "N"), rightlabs= c("Prev.(%)", "95% CI", "w.random"), 
  xlab = "HIV Prevalence (%)", lwd =1, just="right", col.diamond = "black", col.by = "black")
dev.off() 

#g3---Forest plot of HIV prevalence  by national art cov
#presumptive
table(df2b$artcov)

tiff("g3a.tiff", height=20, width=11, units="in", res=300, compression="lzw")
forest(metaprop(e21_HIV._suspects, e20_susp_scrnhiv, studlab= label, title="HIV prevalence in adults with TB symptoms", byvar=artcov, comb.fixed=T, comb.random=T, sm="PAS", data=df2b), 
       sortvar=df2b$p, xlim=c(0, 100), fontsize=14, pscale=100, pooled.totals=T, pooled.events=T, print.tau2=T, print.I2=T, digits=1, 
  leftcols = c("studlab", "n"), 
  rightcols = c("effect", "ci", "w.random"), 
  leftlabs = c("Study", "N"), rightlabs= c("Prev.(%)", "95% CI", "w.random"), 
  xlab = "HIV Prevalence (%)", lwd =1, just="right", col.diamond = "black", col.by = "black")
dev.off() 

#TB patients
tiff("g3b.tiff", height=20, width=11, units="in", res=300, compression="lzw")
forest(metaprop(e28_n_HIVposTB, e27_Tbcases_HIVden, studlab= label, title="HIV prevalence in adults with TB symptoms", byvar=artcov, comb.fixed=T, comb.random=T, sm="PAS", data=df2b), 
       sortvar=df2b$p, xlim=c(0, 100), fontsize=14, pscale=100, pooled.totals=T, pooled.events=T, print.tau2=T, print.I2=T, digits=1, 
  leftcols = c("studlab", "n"), 
  rightcols = c("effect", "ci", "w.random"), 
  leftlabs = c("Study", "N"), rightlabs= c("Prev.(%)", "95% CI", "w.random"), 
  xlab = "HIV Prevalence (%)", lwd =1, just="right", col.diamond = "black", col.by = "black")
dev.off() 

#g5---Forest plot of HIV prevalence  by national symptoms

#presumptive
table(df2b$definition)

tiff("g5a.tiff", height=20, width=11, units="in", res=300, compression="lzw")
forest(metaprop(e21_HIV._suspects, e20_susp_scrnhiv, studlab= label, title="HIV prevalence in adults with TB symptoms", byvar=definition, comb.fixed=T, comb.random=T, sm="PAS", data=df2b), 
       sortvar=df2b$p, xlim=c(0, 100), fontsize=14, pscale=100, pooled.totals=T, pooled.events=T, print.tau2=T, print.I2=T, digits=1, 
  leftcols = c("studlab", "n"), 
  rightcols = c("effect", "ci", "w.random"), 
  leftlabs = c("Study", "N"), rightlabs= c("Prev.(%)", "95% CI", "w.random"), 
  xlab = "HIV Prevalence (%)", lwd =1, just="right", col.diamond = "black", col.by = "black")
dev.off() 

#TB patients
tiff("g5b.tiff", height=20, width=11, units="in", res=300, compression="lzw")
forest(metaprop(e28_n_HIVposTB, e27_Tbcases_HIVden, studlab= label, title="HIV prevalence in adults with TB symptoms", byvar=definition, comb.fixed=T, comb.random=T, sm="PAS", data=df2b), 
       sortvar=df2b$p, xlim=c(0, 100), fontsize=14, pscale=100, pooled.totals=T, pooled.events=T, print.tau2=T, print.I2=T, digits=1, 
  leftcols = c("studlab", "n"), 
  rightcols = c("effect", "ci", "w.random"), 
  leftlabs = c("Study", "N"), rightlabs= c("Prev.(%)", "95% CI", "w.random"), 
  xlab = "HIV Prevalence (%)", lwd =1, just="right", col.diamond = "black", col.by = "black")
dev.off() 

#g5---Forest plot of HIV prevalence in presumptive TB patients by national symptoms

table(df2b$subregion)

df2b$subregion[df2b$subregion=="East Africa"]<-"Central Africa" 
df2b$subregion[df2b$subregion=="Southern Africa"]<-"Central Africa" 
df2b$subregion[df2b$subregion=="West Africa"]<-"Central Africa"
df2b$subregion[df2b$subregion=="Americas"]<-"South-East Asia"
df2b$subregion[df2b$subregion=="Western pacific"]<-"South-East Asia"
df2b$subregion <- factor(as.character(df2b$subregion), levels = c("Central Africa", "South-East Asia"))

#g5---Forest plot of HIV prevalence by subregion

#presumptives
table(df2b$subregion)

tiff("g5a.tiff", height=20, width=11, units="in", res=300, compression="lzw")
forest(metaprop(e21_HIV._suspects, e20_susp_scrnhiv, studlab= label, title="HIV prevalence in adults with TB symptoms", byvar=subregion, comb.fixed=T, comb.random=T, sm="PAS", data=df2b), 
       sortvar=df2b$p, xlim=c(0, 100), fontsize=14, pscale=100, pooled.totals=T, pooled.events=T, print.tau2=T, print.I2=T, digits=1, 
  leftcols = c("studlab", "n"), 
  rightcols = c("effect", "ci", "w.random"), 
  leftlabs = c("Study", "N"), rightlabs= c("Prev.(%)", "95% CI", "w.random"), 
  xlab = "HIV Prevalence (%)", lwd =1, just="right", col.diamond = "black", col.by = "black")
dev.off() 

#TB patients
tiff("g5b.tiff", height=20, width=11, units="in", res=300, compression="lzw")
forest(metaprop(e28_n_HIVposTB, e27_Tbcases_HIVden, studlab= label, title="HIV prevalence in adults with TB symptoms", byvar=subregion, comb.fixed=T, comb.random=T, sm="PAS", data=df2b), 
       sortvar=df2b$p, xlim=c(0, 100), fontsize=14, pscale=100, pooled.totals=T, pooled.events=T, print.tau2=T, print.I2=T, digits=1, 
  leftcols = c("studlab", "n"), 
  rightcols = c("effect", "ci", "w.random"), 
  leftlabs = c("Study", "N"), rightlabs= c("Prev.(%)", "95% CI", "w.random"), 
  xlab = "HIV Prevalence (%)", lwd =1, just="right", col.diamond = "black", col.by = "black")
dev.off() 

#g6---Forest plot of HIV prevalence by year

table(df2b$midyr)

#presumptive
tiff("g6a.tiff", height=20, width=11, units="in", res=300, compression="lzw")
forest(metaprop(e21_HIV._suspects, e20_susp_scrnhiv, studlab= label, title="HIV prevalence in adults with TB symptoms", byvar=midyr, comb.fixed=T, comb.random=T, sm="PAS", data=df2b), 
       sortvar=df2b$p, xlim=c(0, 100), fontsize=14, pscale=100, pooled.totals=T, pooled.events=T, print.tau2=T, print.I2=T, digits=1, 
  leftcols = c("studlab", "n"), 
  rightcols = c("effect", "ci", "w.random"), 
  leftlabs = c("Study", "N"), rightlabs= c("Prev.(%)", "95% CI", "w.random"), 
  xlab = "HIV Prevalence (%)", lwd =1, just="right", col.diamond = "black", col.by = "black")
dev.off()

#TB patients
tiff("g6b.tiff", height=20, width=11, units="in", res=300, compression="lzw")
forest(metaprop(e28_n_HIVposTB, e27_Tbcases_HIVden, studlab= label, title="HIV prevalence in adults with TB symptoms", byvar=midyr, comb.fixed=T, comb.random=T, sm="PAS", data=df2b), 
       sortvar=df2b$p, xlim=c(0, 100), fontsize=14, pscale=100, pooled.totals=T, pooled.events=T, print.tau2=T, print.I2=T, digits=1, 
  leftcols = c("studlab", "n"), 
  rightcols = c("effect", "ci", "w.random"), 
  leftlabs = c("Study", "N"), rightlabs= c("Prev.(%)", "95% CI", "w.random"), 
  xlab = "HIV Prevalence (%)", lwd =1, just="right", col.diamond = "black", col.by = "black")
dev.off() 


```

##discussion figure

```{r}
table(df2b$popHIVprev)
table(df2b$artcov)
#cell A
df4a<- subset(df2b, popHIVprev== "low (0-5%)" & artcov== "low (0-40%)")
#general pop
mean(df4a$e50_subHIV_perc)
error <- qt(0.975,df=length(df4a$e50_subHIV_perc)-1)*sd(df4a$e50_subHIV_perc)/sqrt(length(df4a$e50_subHIV_perc))
error

lowera<-mean(df4a$e50_subHIV_perc)-error
lowera
uppera<-mean(df4a$e50_subHIV_perc)+error
uppera

#cell b
df4b<- subset(df2b, popHIVprev== "low (0-5%)" & artcov== "moderate(40-81%)")
#general pop
mean(df4b$e50_subHIV_perc)
errorb <- qt(0.975,df=length(df4b$e50_subHIV_perc)-1)*sd(df4b$e50_subHIV_perc)/sqrt(length(df4b$e50_subHIV_perc))
errorb

lowerb<-mean(df4b$e50_subHIV_perc)-error
lowerb
upperb<-mean(df4b$e50_subHIV_perc)+error
upperb

#cell c
df4c<- subset(df2b, popHIVprev== "high(5-30%)" & artcov== "low (0-40%)")

#general pop
mean(df4c$e50_subHIV_perc)
errorc <- qt(0.975,df=length(df4c$e50_subHIV_perc)-1)*sd(df4c$e50_subHIV_perc)/sqrt(length(df4c$e50_subHIV_perc))
errorc

lowerc<-mean(df4c$e50_subHIV_perc)-error
lowerc
upperc<-mean(df4c$e50_subHIV_perc)+error
upperc

#cell d
#general pop
df4d<- subset(df2b, popHIVprev== "high(5-30%)" & artcov== "moderate(40-81%)")
mean(df4d$e50_subHIV_perc)
errord <- qt(0.975,df=length(df4d$e50_subHIV_perc)-1)*sd(df4d$e50_subHIV_perc)/sqrt(length(df4d$e50_subHIV_perc))
errord

lowerd<-mean(df4d$e50_subHIV_perc)-error
lowerd
upperd<-mean(df4d$e50_subHIV_perc)+error
upperd

df5a<- subset(df2b, popHIVprev== "low (0-5%)")
#suspects
tiff("f5a.tiff", height=20, width=11, units="in", res=300, compression="lzw")
forest(metaprop(e21_HIV._suspects, e20_susp_scrnhiv, studlab= label, title="HIV prevalence in adults with TB symptoms", byvar=artcov, comb.fixed=T, comb.random=T, sm="PAS", data=df5a), 
       sortvar=df5a$p, xlim=c(0, 100), fontsize=14, pscale=100, pooled.totals=T, pooled.events=T, print.tau2=T, print.I2=T, digits=1, 
  leftcols = c("studlab", "n"), 
  rightcols = c("effect", "ci", "w.random"), 
  leftlabs = c("Study", "N"), rightlabs= c("Prev.(%)", "95% CI", "w.random"), 
  xlab = "HIV Prevalence (%)", lwd =1, just="right", col.diamond = "black", col.by = "black")
dev.off() 

df5b<- subset(df2b, popHIVprev== "high(5-30%)")
#suspects
tiff("f5b.tiff", height=20, width=11, units="in", res=300, compression="lzw")
forest(metaprop(e21_HIV._suspects, e20_susp_scrnhiv, studlab= label, title="HIV prevalence in adults with TB symptoms", byvar=artcov, comb.fixed=T, comb.random=T, sm="PAS", data=df5b), 
       sortvar=df5b$p, xlim=c(0, 100), fontsize=14, pscale=100, pooled.totals=T, pooled.events=T, print.tau2=T, print.I2=T, digits=1, 
  leftcols = c("studlab", "n"), 
  rightcols = c("effect", "ci", "w.random"), 
  leftlabs = c("Study", "N"), rightlabs= c("Prev.(%)", "95% CI", "w.random"), 
  xlab = "HIV Prevalence (%)", lwd =1, just="right", col.diamond = "black", col.by = "black")
dev.off() 

#TB patients
df6a<- subset(df2b, popHIVprev== "low (0-5%)")
#suspects
tiff("f6a.tiff", height=20, width=11, units="in", res=300, compression="lzw")
forest(metaprop(e28_n_HIVposTB, e27_Tbcases_HIVden, studlab= label, title="HIV prevalence in adults with TB symptoms", byvar=artcov, comb.fixed=T, comb.random=T, sm="PAS", data=df6a), 
       sortvar=df6a$p, xlim=c(0, 100), fontsize=14, pscale=100, pooled.totals=T, pooled.events=T, print.tau2=T, print.I2=T, digits=1, 
  leftcols = c("studlab", "n"), 
  rightcols = c("effect", "ci", "w.random"), 
  leftlabs = c("Study", "N"), rightlabs= c("Prev.(%)", "95% CI", "w.random"), 
  xlab = "HIV Prevalence (%)", lwd =1, just="right", col.diamond = "black", col.by = "black")
dev.off() 

df6b<- subset(df2b, popHIVprev== "high(5-30%)")
#patients
tiff("f6b.tiff", height=20, width=11, units="in", res=300, compression="lzw")
forest(metaprop(e28_n_HIVposTB, e27_Tbcases_HIVden, studlab= label, title="HIV prevalence in adults with TB symptoms", byvar=artcov, comb.fixed=T, comb.random=T, sm="PAS", data=df6b), 
       sortvar=df6b$p, xlim=c(0, 100), fontsize=14, pscale=100, pooled.totals=T, pooled.events=T, print.tau2=T, print.I2=T, digits=1, 
  leftcols = c("studlab", "n"), 
  rightcols = c("effect", "ci", "w.random"), 
  leftlabs = c("Study", "N"), rightlabs= c("Prev.(%)", "95% CI", "w.random"), 
  xlab = "HIV Prevalence (%)", lwd =1, just="right", col.diamond = "black", col.by = "black")
dev.off() 


#dodge graph

rateg<-read.csv("error_table.csv", stringsAsFactors=T)
str(rateg)

rateg$artcov<-factor(rateg$artcov, levels=c(1:2),labels=c("low","high"))
rateg$group<-factor(rateg$group, levels=c(1:3),labels=c("general","presumptive", "tbpatient"))

dodge <- position_dodge(width =0.7)

ggplot(rateg, aes(x=group, y=mean, group=artcov, colour=artcov, linetype=artcov, shape=artcov)) +   geom_errorbar(position = dodge, aes(ymin=lower, ymax=upper), width=0.4, size=1)+
  theme_bw()+
  scale_linetype_manual(values=c("solid", "solid"))+
  #geom_hline(yintercept=1, linetype="dotted")+
  scale_color_manual(values=c("firebrick", "steelblue"))+
  scale_y_continuous(limits=c(0,100), breaks = c(0,25,50,75,100), minor_breaks = seq(0,100, 5))+
  #scale_x_continuous(breaks = c(1,2,3))+
  scale_shape_manual(values=c(19, 19))+
  #labs(title="TB case notification rates\n (by HIV status and gender)") + 
  #theme(legend.position = c(0.8, 0.8)) +
  #labs(y = "HIV positive to HIV negative \n TB incidence rate ratio (95% CI)") +
  #labs(x = "Age group (years)") + 
  theme(axis.text.y=element_text(size=15)) +
  theme(axis.text.x=element_text(size=12, angle = 0)) +
  theme(axis.title.y=element_text(size=17)) + 
  theme(axis.title.x=element_text(size=15))+
  geom_point(size=3, fill="white", position = dodge)+
  guides(color=guide_legend("artcov"))+
  facet_grid(. ~subhiv)
  
ggsave("rateg.png", dpi = 600)


```

